An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Hope there's no conflicts
Looking at some of the changes in Sec 3 and finiteness

  For the converse, suppose $L$ has a polyhedral Bayes risk.

  implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
  We now show $\Sc$ is a minimum representative set.

@@

  If $\Sc$ was not a \emph{minimum} representative set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
  By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
  There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
  We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
  By construction of $\Sc$, we must have only added at most one of these to the set.
  Therefore, $\Sc$ is a minimum representative set.

@@

\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  For any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
  Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
\end{lemma}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite minimum representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
  Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
  Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
  Thus, every level set of $\Gamma$ is a cell in the induced power diagram.

  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
\end{proof}
\begin{corollary}\label{cor:finite-minrep-trim}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
\end{corollary}
\begin{proof}
  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
n  Let $r\in\R$ be arbitrary.
  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
\end{proof}
\begin{corollary}\label{cor:finite-rep-contains-min}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
  Then $\R'$ contains a minimum representative set.
  \raf{Let's state this in the main part for losses too}
\end{corollary}
\begin{proof}
  TBD
\end{proof}
\begin{corollary}\label{cor:finite-embed-min-rep}
  Let elicitable $\Gamma : \simplex \toto \reals^d$ embed a finite elicitable property $\gamma:\simplex\toto\R$ via embedding $\varphi$.
  Then $\Sc$ is a minimum representative set for $\gamma$ if and only if $\varphi(\Sc)$ is a minimum representative set for $\Gamma$
\end{corollary}
\begin{proof}
  TBD
  \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
  \jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$. This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum. }
  \raf{Use Proposition~\ref{prop:SL-minimum}?}
\end{proof}

>>>>

  For the converse, suppose $L$ has a polyhedral Bayes risk, which implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
  since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
  Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
  Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
  Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
  We now show $\Sc$ is a minimum representative set.

@@

  If $\Sc$ was not a \emph{minimum} representative set \jessiet{minimal proof, not minimum}, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
  By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
  There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
  We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
  By construction of $\Sc$, we must have only added at most one of these to the set.
  Therefore, $\Sc$ is a minimum representative set.

@@

\begin{lemma}\label{lem:finite-minrep-weakly-dominate}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
  There is a minimum representative set $\R^* \subseteq \R'$.
  Additionally, for any $r \in \R \setminus \R^*$, there is a $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
  Moreover, the level sets $\{\Gamma_{r^*} \mid r^* \in \R^*\}$ are the unique full-dimensional level sets of $\Gamma$.
\end{lemma}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  By Proposition~\ref{prop:SL-minimum}, since $L$ has a finite representative set, $-\risk{L}$ is polyhedral, with epigraph $E_L$.
  Observe that for any report $r \in \R$, the hyperplane $H^L_r : p \mapsto (p, -\inprod{p}{L(r)})$ supports $E_L$ exactly when $p\in\Gamma_r$.
  Since $E_L$ is a convex polyhedron in $\reals^{n+1}$, we can take a linear projection of the faces of $E_L$ onto $\simplex \subset \reals^n$ to yield an affinely equivalent cell complex $C$ (Definition~\ref{def:cell-complex}), which is a power diagram by Theorem~\ref{thm:aurenhammer}.
  Thus, every level set of $\Gamma$ is a cell in the induced power diagram.

  Consider any minimum representative set $\R^*$; we claim $\R^* \subseteq \R'$.
  Since the level sets of $\Gamma$ are cells in an induced power diagram, the intersection of any two level sets have pairwise disjoint relative interiors (Def.~\ref{def:cell-complex}).
  Therefore, any representative $\R^*$ with smaller cardinality than $\R'$ must be a subset of $\R'$ since no level set can span the relative interiors of any other level set.

  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
\end{proof}
\begin{corollary}\label{cor:finite-minrep-trim}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
\end{corollary}
\begin{proof}
  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
  Let $r\in\R$ be arbitrary.
  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
\end{proof}

\jessiet{Combining commented corollary into Lemma~\ref{lem:finite-minrep-weakly-dominate} because we need $\R^*$ to be minimum for the later parts of the statement.}
%\begin{corollary}\label{cor:finite-rep-contains-min}
%  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
%  Then $\R'$ contains a minimum representative set.
%  \raf{Let's state this in the main part for losses too}
%\end{corollary}
%\begin{proof}
%  By assumption, 
%  \begin{itemize}
%  	\item $\{\Gamma_r \mid r \in \R'\}$ is a finitely generated set.
%  \end{itemize}
%  Therefore, $\R^* \subset \R'$ is minimum, meaning.  
%\end{proof}

\begin{corollary}\label{cor:finite-embed-min-rep}
  Let elicitable $\Gamma : \simplex \toto \reals^d$ embed a finite elicitable property $\gamma:\simplex\toto\R$ via embedding $\varphi$.
  Then $\Sc$ is a minimum representative set for $\gamma$ if and only if $\varphi(\Sc)$ is a minimum representative set for $\Gamma$
\end{corollary}
\begin{proof}
  Suppose $\Gamma := \prop{L}$ and $\gamma := \prop{\ell}$.
  Let $\Sc$ be a finite represntative set for $\gamma$.
  By the embedding condition (ii.) we know that $\varphi(\Sc)$ is a finite representative set for $\Gamma$.
  To observe that both are minimum if and only if the other is, since both have finite representative sets, both $E_L$ and $E_\ell$ are polyhedral.
  \jessie{Part about bijection from facets of $E_L$ in Prop 1 removed. Any reason why?}
  \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
  \jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$. This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum. }
  \raf{Use Proposition~\ref{prop:SL-minimum}?}
\end{proof}
